\bfseries\LARGE\singlespacing{Transmission of respiratory viral infections with and without air cleaners in a Swiss school under non-pandemic conditions in 2023: A modeling study of epidemiological, environmental, and molecular data}

### 2023-10-16 doc/paper/manuscript-lancet.tex

\begin{figure}[!htpb]
    \centering
    \includegraphics{../../results/mol-data/saliva-distribution.pdf}
    \includegraphics{../../results/mol-data/network-plot.pdf}
    \caption{\textbf{Molecular detection of respiratory viruses and transmission network based on spatiotemporal analysis of students' saliva samples}. \textbf{(a)}~Number of positive saliva samples by virus. \textbf{(b)}~Daily number of positive saliva samples (colored circles) and possible transmission chains within classes (directed arrows). Positive samples are linked if they belong to the same virus and are less than 1~week apart. Positive samples from the air and filters as blank squares aligned. Flu B: Influenza B, HRV: rhinovirus, AdV: adenovirus, CoV: SARS-CoV-2, MPV: metapneumovirus, PIV: parainfluenza virus.}
    \label{fig:molecular-descriptives}
\end{figure}

@@

\begin{figure}[!htpb]
\centering
    \includegraphics{../../results/mol-data/saliva-by-study-condition.pdf}
    \includegraphics{../../results/env-data/aerosol-number-boxplot.pdf}
    \includegraphics{../../results/epi-data/cases_by_condition.pdf}
    \includegraphics{../../results/cough-data/coughs-frequency-by-condition.pdf}
    \caption{\textbf{Risk of infection by study condition}. \textbf{(a)}~Number of positive saliva samples. \textbf{(b)}~Daily average aerosol number concentrations as boxplots. \textbf{(c)}~Number of respiratory cases. \textbf{(d)}~Daily average number of detected coughs per minute.}
    \label{fig:infection-risk}
\end{figure}

>>>>

\begin{figure}[!htpb]
    \centering
    \includegraphics{../../results/mol-data/saliva-distribution.pdf}\hspace{.5cm}
    \includegraphics{../../results/mol-data/network-plot.pdf}
    \caption{\textbf{Molecular detection of respiratory viruses and transmission network based on spatiotemporal analysis of students' saliva samples}. \textbf{(a)}~Number of positive saliva samples by virus. \textbf{(b)}~Daily number of positive saliva samples (colored circles) and possible transmission chains within classes (directed arrows). Positive samples are linked if they belong to the same virus and are less than 1~week apart. Positive samples from the air and filters as blank squares aligned. Flu B: Influenza B, HRV: rhinovirus, AdV: adenovirus, CoV: SARS-CoV-2, MPV: metapneumovirus, PIV: parainfluenza virus.}
    \label{fig:molecular-descriptives}
\end{figure}

@@

\begin{figure}[!htpb]
\centering
    \includegraphics{../../results/mol-data/saliva-by-study-condition.pdf}\hspace{1.5cm}
    \includegraphics{../../results/env-data/aerosol-number-boxplot.pdf}
    \includegraphics{../../results/epi-data/cases_by_condition.pdf}\hspace{1.5cm}
    \includegraphics{../../results/cough-data/coughs-frequency-by-condition.pdf}
    \caption{\textbf{Risk of infection by study condition}. \textbf{(a)}~Number of positive saliva samples. \textbf{(b)}~Daily average aerosol number concentrations as boxplots. \textbf{(c)}~Number of respiratory cases. \textbf{(d)}~Daily average number of detected coughs per minute.}
    \label{fig:infection-risk}
\end{figure}
